Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-27 analysis/paper/hotspots-paper.Rmd
reordered output formats; added ggplotly calls

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
output: 
  - bookdown::html_document2
  - github_document:
      toc: true
      toc_depth: 2
---

@@

```{r scatter-2}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol == keller_mediator, nonlocal = nonlocal_symbol), size = 0.05) + theme(legend.position = "none") + xlab("Pleiotropy LOD") + ylab("Mediation LOD difference")
fnsvg <- paste0("Chr", hot_chr, "_scatter.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter.pdf")
ggsave(plot = p, filename = here("analysis", "figures", fnsvg))
ggsave(plot = p, filename = here("analysis", "figures", fnpdf))
p
```

```{r scatter_by_local-2}
foo <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id)
foo %>%
  ggplot() +
  geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = nonlocal_symbol, nonlocal = nonlocal_symbol), size = 0.1) +
  facet_wrap(. ~ local_symbol, nrow = ceiling(nlocal / 2), ncol = 2) +
  broman::karl_theme(strip.placement = "inside") +
  theme(legend.position = "none") +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
) +
  xlab("Pleiotropy LOD") +
  ylab("Mediation LOD difference") +
  geom_text(aes(x = 1, y = 1, label = local_symbol), inherit.aes=FALSE)

fnsvg <- paste0("Chr", hot_chr, "_scatter-panel.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter-panel.pdf")
ggsave(filename = here("analysis", "figures", fnsvg), height = ceiling(nlocal / 2))
ggsave(filename = here("analysis", "figures", fnpdf), height = ceiling(nlocal / 2))

# put in multiple figures, if there are many local traits
n_figs <- 1 + nlocal %/% 18 # 18 is the number of panels per page in pdf
n_last <- nlocal %% 18 # number of panels on last figure
max_pleio_lod <- max(foo$pleiotropy_lod)
max_med_lod_difference <- max(foo$lod_diff)
min_med_lod_difference <- min(foo$lod_diff)

@@

```{r heat9-2, eval = !file.exists(fnhtml)}
ord <- match(rn, rownames(pm))

p <- pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = tibble(local = scols1[ord]),
            limits = c(0, 5)
            ) %>%
  hide_guides()
fnpdf <- here("analysis", "figures", paste0("Chr", hot_chr, "hm.pdf"))
htmlwidgets::saveWidget(widget = p,
                        file = fnhtml
                        )
webshot::webshot(url = fnhtml,
                 file = fnpdf,
                 cliprect = "viewport"
                 )
```

```{r heat10-2}
webshot::webshot(fnhtml)
```

@@

@@

```{r heat9-5, ref.label = "heat9-2", eval = !file.exists(fnhtml)}
```

@@

@@

```{r heat9-7, ref.label = "heat9-2", eval = !file.exists(fnhtml)}
```

@@

@@

```{r heat9-11, ref.label = "heat9-2", eval = !file.exists(fnhtml)}
```

@@

@@

```{r heat9-13, ref.label = "heat9-2", eval = !file.exists(fnhtml)}
```

>>>>

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
output: 
  - github_document:
      toc: true
      toc_depth: 2
  - bookdown::html_document2
---

@@

```{r scatter-2}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol == keller_mediator, nonlocal = nonlocal_symbol), size = 0.05) + theme(legend.position = "none") + xlab("Pleiotropy LOD") + ylab("Mediation LOD difference")
fnsvg <- paste0("Chr", hot_chr, "_scatter.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter.pdf")
ggsave(plot = p, filename = here("analysis", "figures", fnsvg))
ggsave(plot = p, filename = here("analysis", "figures", fnpdf))
plotly::ggplotly(p)
```

```{r scatter_by_local-2, fig.height = ceiling(nlocal / 2)}
foo <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id)
p <- foo %>%
  ggplot() +
  geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = nonlocal_symbol, nonlocal = nonlocal_symbol), size = 0.1) +
  facet_wrap(. ~ local_symbol, nrow = ceiling(nlocal / 2), ncol = 2) +
  broman::karl_theme(strip.placement = "inside") +
  theme(legend.position = "none") +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
) +
  xlab("Pleiotropy LOD") +
  ylab("Mediation LOD difference") +
  geom_text(aes(x = 1, y = 1, label = local_symbol), inherit.aes=FALSE)

fnsvg <- paste0("Chr", hot_chr, "_scatter-panel.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter-panel.pdf")
ggsave(p, filename = here("analysis", "figures", fnsvg), height = ceiling(nlocal / 2))
ggsave(p, filename = here("analysis", "figures", fnpdf), height = ceiling(nlocal / 2))
plotly::ggplotly(p)
```

```{r multipanel_scatter-2, eval = FALSE}
# put in multiple figures, if there are many local traits
n_figs <- 1 + nlocal %/% 18 # 18 is the number of panels per page in pdf
n_last <- nlocal %% 18 # number of panels on last figure
max_pleio_lod <- max(foo$pleiotropy_lod)
max_med_lod_difference <- max(foo$lod_diff)
min_med_lod_difference <- min(foo$lod_diff)

@@

```{r heat9-2, eval = TRUE}
ord <- match(rn, rownames(pm))

(p <- pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = tibble(local = scols1[ord]),
            limits = c(0, 5)
            ) %>%
  hide_guides()
)
fnpdf <- here("analysis", "figures", paste0("Chr", hot_chr, "hm.pdf"))
htmlwidgets::saveWidget(widget = p, 
                        file = fnhtml
                        )
```

```{r webshot-2, eval = FALSE}
webshot::webshot(url = fnhtml,
                 file = fnpdf,
                 cliprect = "viewport"
                 )
```

```{r heat10-2, eval = FALSE}
webshot::webshot(fnhtml)
```

@@

```{r multipanel_scatter-5, ref.label = "multipanel_scatter-2", eval = FALSE}
```

@@

```{r heat9-5, ref.label = "heat9-2", eval = TRUE}
```

@@

```{r multipanel_scatter-7, ref.label = "multipanel_scatter-2", eval = FALSE}
```

@@

```{r heat9-7, ref.label = "heat9-2", eval = TRUE}
```

@@

```{r multipanel_scatter-11, ref.label = "multipanel_scatter-2", eval = FALSE}
```

@@

```{r heat9-11, ref.label = "heat9-2", eval = TRUE}
```

@@

```{r multipanel_scatter-13, ref.label = "multipanel_scatter-2", eval = FALSE}
```

@@

```{r heat9-13, ref.label = "heat9-2", eval = TRUE}
```
